\large How resource abundance and stochasticity affect animals' space-use requirements

### 2023-09-09 writing/appendix-1-concepts-and-definitions.Rmd
removed bold because all figures have unicode

---
title: \large How resource abundance and stochasticity affect animals' spatial needs
subtitle: "Appendix 1: Concepts and definitions"
author:
  - name: Stefano Mezzini
    email: stefano.mezzini@ubc.ca
    institute: [braes, biol]
  - name: Simon Wood
    institute: uofe
  - name: Chris H. Fleming
    institute: [ucf, smith]
  - name: E. Patrícia Medici
    institute: [tapir, iucn, escas]
  - name: Michael J. Noonan
    email: michael.noonan@ubc.ca
    institute: [braes, biol, cmps]
institute:
  - braes: Okanagan Institute for Biodiversity, Resilience, and Ecosystem Services, The University of British Columbia Okanagan, Kelowna, British Columbia, Canada.
  - biol: Department of Biology, The University of British Columbia Okanagan, Kelowna, British Columbia, Canada.
  - uofe: School of Mathematics, James Clerk Maxwell Building, University of Edinburgh, Edinburgh, Unted Kingdom.
  - ucf: Department of Biology, University of Central Florida, Orlando, Florida 32816, United States.
  - smith: Smithsonian Conservation Biology Institute, National Zoological Park, 1500 Remount Rd., Front Royal, VA 22630, United States.
  - tapir: Lowland Tapir Conservation Initiative (LTCI), Instituto de Pesquisas Ecológicas (IPÊ), Rodovia Dom Pedro I, km 47, Nazaré Paulista, São Paulo 12960-000, Brazil.
  - iucn: IUCN SSC Tapir Specialist Group (TSG), Campo Grande, Brazil.
  - escas: Escola Superior de Conservação Ambiental E Sustentabilidade (ESCAS/IPÊ), Rodovia Dom Pedro I, km 47, Nazaré Paulista, São Paulo 12960-000, Brazil.
  - cmps: Department of Computer Science, Math, Physics, and Statistics, The University of British Columbia Okanagan, Kelowna, British Columbia, Canada.
bibliography: 'hr-resource-stoch.bib'
csl: 'the-american-naturalist.csl'
fontsize: 12pt
indent: true
header-includes:
    - \usepackage{setspace}\doublespacing # for double-spaced text
    - \usepackage[small]{titlesec} # for smaller font for headings
    - \usepackage{caption} # for more customization of captions
    - \captionsetup[figure]{font=scriptsize} # smaller caption text
    - \usepackage{hanging} # for hanging indents in references
subparagraph: true # needed for \usepackage[small]{titlesec}
output:
  bookdown::pdf_document2:
    number_sections: false
    toc: false
    pandoc_args:
      - '--lua-filter=scholarly-metadata.lua' # for author affiliations
      - '--lua-filter=author-info-blocks.lua' # for author affiliations
---

>>>>

---
title: \large How resource abundance and stochasticity affect animals' space-use requirements
subtitle: "Appendix 1: Concepts and definitions"
author:
  - name: Stefano Mezzini
    email: stefano.mezzini@ubc.ca
    institute: [braes, biol]
  - name: Simon Wood
    institute: uofe
  - name: Chris H. Fleming
    institute: [ucf, smith]
  - name: E. Patrícia Medici
    institute: [tapir, iucn, escas]
  - name: Michael J. Noonan
    email: michael.noonan@ubc.ca
    institute: [braes, biol, cmps]
institute:
  - braes: Okanagan Institute for Biodiversity, Resilience, and Ecosystem Services, The University of British Columbia Okanagan, Kelowna, British Columbia, Canada.
  - biol: Department of Biology, The University of British Columbia Okanagan, Kelowna, British Columbia, Canada.
  - uofe: School of Mathematics, James Clerk Maxwell Building, University of Edinburgh, Edinburgh, Unted Kingdom.
  - ucf: Department of Biology, University of Central Florida, Orlando, Florida 32816, United States.
  - smith: Smithsonian Conservation Biology Institute, National Zoological Park, 1500 Remount Rd., Front Royal, VA 22630, United States.
  - tapir: Lowland Tapir Conservation Initiative (LTCI), Instituto de Pesquisas Ecológicas (IPÊ), Rodovia Dom Pedro I, km 47, Nazaré Paulista, São Paulo 12960-000, Brazil.
  - iucn: IUCN SSC Tapir Specialist Group (TSG), Campo Grande, Brazil.
  - escas: Escola Superior de Conservação Ambiental E Sustentabilidade (ESCAS/IPÊ), Rodovia Dom Pedro I, km 47, Nazaré Paulista, São Paulo 12960-000, Brazil.
  - cmps: Department of Computer Science, Math, Physics, and Statistics, The University of British Columbia Okanagan, Kelowna, British Columbia, Canada.
bibliography: 'hr-resource-stoch.bib'
csl: 'the-american-naturalist.csl'
fontsize: 12pt
indent: true
header-includes:
    - \usepackage{setspace}\doublespacing # for double-spaced text
    - \usepackage[small]{titlesec} # for smaller font for headings
    - \usepackage{caption} # for more customization of captions
    - \captionsetup[figure]{font=scriptsize} # smaller caption text
    - \usepackage{hanging} # for hanging indents in references
subparagraph: true # needed for \usepackage[small]{titlesec}
output:
  bookdown::pdf_document2:
    number_sections: false
    toc: false
    pandoc_args:
      - '--lua-filter=scholarly-metadata.lua' # for author affiliations
      - '--lua-filter=author-info-blocks.lua' # for author affiliations
---

### 2023-09-09 writing/appendix-2-simulations.Rmd
removed bold because all figures have unicode

---
title: \large How resource abundance and stochasticity affect animals' spatial needs
subtitle: "Appendix 2: Simulations"
author:
  - name: Stefano Mezzini
    email: stefano.mezzini@ubc.ca
    institute: [biol, braes]
  - name: Simon Wood
    institute: uofe
  - name: E. Patrícia Medici
    institute: [tapir, iucn, escas]
  - name: Michael J. Noonan
    email: michael.noonan@ubc.ca
    institute: [biol, braes, cmps]
institute:
  - biol: Department of Biology, The University of British Columbia Okanagan, Kelowna, British Columbia, Canada.
  - braes: Okanagan Institute for Biodiversity, Resilience, and Ecosystem Services, The University of British Columbia Okanagan, Kelowna, British Columbia, Canada.
  - uofe: School of Mathematics, James Clerk Maxwell Building, University of Edinburgh, Edinburgh, Unted Kingdom.
  - tapir: Lowland Tapir Conservation Initiative (LTCI), Instituto de Pesquisas Ecológicas (IPÊ), Rodovia Dom Pedro I, km 47, Nazaré Paulista, São Paulo 12960-000, Brazil.
  - iucn: IUCN SSC Tapir Specialist Group (TSG), Campo Grande, Brazil.
  - escas: Escola Superior de Conservação Ambiental E Sustentabilidade (ESCAS/IPÊ), Rodovia Dom Pedro I, km 47, Nazaré Paulista, São Paulo 12960-000, Brazil.
  - cmps: Department of Computer Science, Math, Physics, and Statistics, The University of British Columbia Okanagan, Kelowna, British Columbia, Canada.
bibliography: 'hr-resource-stoch.bib'
csl: 'the-american-naturalist.csl'
fontsize: 12pt
header-includes:
    - \usepackage{setspace}\doublespacing # for double-spaced text
    - \usepackage[small]{titlesec} # for smaller font for headings
    - \usepackage{caption} # for more customization of captions
    - \captionsetup[figure]{font=scriptsize} # smaller caption text
    - \usepackage{hanging} # for hanging indents in references
subparagraph: true # needed for \usepackage[small]{titlesec}
output:
  bookdown::pdf_document2:
    toc: false
    pandoc_args:
      - '--lua-filter=scholarly-metadata.lua' # for author affiliations
      - '--lua-filter=author-info-blocks.lua' # for author affiliations
---

@@

```{r 5-5-sims, eval=TRUE, echo=FALSE, fig.cap="Simulated home range sizes, $H$, of an organism living in habitats where the mean and variance in resources are constant, linearly increasing, cyclical, drifting, or erratic over time (and homogenous over space). Note how $H$ decreases nonlinearly as $\\mu(t)$ increases and increases nonlinearly as $\\sigma^2(t)$ increases. Additionally, the variance in $H$ is higher when $\\mu(t)$ is lower or $\\sigma^2(t)$ is higher, and changes in $\\sigma^2(t)$ have greater impacts when $\\mu(t)$ is low.", out.width='100%'}
knitr::include_graphics('H:/GitHub/hr-resource-stoch/figures/mean-variance-5-by-5-hr-sims.png',
                        rel_path = FALSE)
```

```{r 5-5-reg, eval=TRUE, echo=FALSE, fig.cap="Effects of $\\e(R)$ and $\\var(R)$ on simulated spatial requirements. The relationships were estimated using a Generalized Additive Model for Location and Scale (GAMLS; Rigby and Stasinopoulos 2005; Stasinopoulos and Rigby 2007) with a Gamma location-scale family of distributions ($\\tt{mgcv\\!::\\!gammals})$. The model accounted for the effects of $\\e(R)$ and $\\var(R)$ and the interaction effects between the two on both the location (i.e., mean) of $H$ and its scale parameter. Note the nonlinear decrease in $H$ as $\\e(R)$ increases and the increase in $H$ as $\\var(R)$ increases. Additionally, note how the variance in spatial needs strongly increases with mean spatial needs.", out.width='100%'}
knitr::include_graphics('H:/GitHub/hr-resource-stoch/figures/simulation-regression-plots.png',
                        rel_path = FALSE)
```

@@

```{r sims-example, echo=FALSE, eval=TRUE, fig.cap="Overview of how animals' spatial needs were simulated. (a.) Tracks were simulated using an Integrated Ornstein-Uhlenbeck model (IOU model, an infinitely diffusive and continous-velocity movement model), starting from the point $\\langle 0, 0 \\rangle$ (black and yellow square). (b.) Each time the track crossed into a new cell (green dots), the animal collected a random amount of resources that followed a Gamma distribution with common mean $\\mu (t)$ and variance $\\sigma^2 (t)$. (c.) Each time the animal collected more resources, its satiety (purple) increased. Once the animal collected sufficient resources, the animal stopped moving (i.e., the track was truncated). (d.) The process was repeated $2^{10}=1024$ times (13 tracks pictured in this panel). (e.) The final set of (truncated) tracks was then modeled using Ornstein-Uhlenbeck Foraging models to estimate the 95\\% home range estimates using Autocorrelated Kernel Density Estimates.", out.width='100%', fig.pos='!h'}
knitr::include_graphics('H:/GitHub/hr-resource-stoch/figures/simulation-example.png',
                        rel_path = FALSE)
```

@@

```{r dt-sensitivity, fig.cap="Exploratory plots used to decide an appropriate sampling interval. (a.) Histograms of the number of encounters as a function of the interval between encounters, with a binwith of 30 seconds. Although some encounters occur with less than 30 seconds between them, approximately 93\\% of them occur at least 30 seconds apart. (b.) Number of detected encounters as a function of sampling interval. The colored lines indicate the estimated relationship based on a Generalized Additive Model fit using the $\\tt{geom\\_smooth}$ function from the $\\tt{ggplot2}$ package. Although the number of encounters detected decreases as sampling interval doubles, the loss at $\\Delta = 30$s is negligible. (c.) Beginning of the track generated with seed \"1\" (purple line) for different sampling intervals. Red dots indicate locations where the animal remained in the same cell, while the blue squares indicate when an animal was in a new cell and thus encountered food. While the number of encounters detected decreases as the sampling interval increases, most of the encounters lost at $\\Delta t = 30$s occured because the animal remained almost adjacent to the borders between cells. Additionally, the track at $\\Delta t = 30$s is still sufficiently tortuous to represent realistic animal movement. (d.) The three tracks used in these tests over the raster used for determining when the animals encountered food.", out.width='100%', echo=FALSE, eval=TRUE}
knitr::include_graphics('H:/GitHub/hr-resource-stoch/figures/thinning-examples.png',
                        rel_path = FALSE)
```

@@

In this script, we check how many tracks are necessary to produce stable and accurate estimates of the spatial needs. We do so by estimating the home ranges of animals for varying numbers of track in the best-case scenario (highest $\e(R)$ and lowest $\var(R)$) and worst-case scenario (lowest $\e(R)$ and highest $\var(R)$).

@@

ggplot(saturation_days, aes(n_days, hr)) +
  facet_wrap(~ case, nrow = 1) +
  geom_vline(xintercept = 100, color = 'darkorange') +
  geom_smooth(method = 'gam', color = 'black',
              formula = y ~ s(x, bs = 'cs', k = 10),
              method.args = list(family = Gamma(link = 'log'))) +
  geom_point(alpha = 0.3) +
  scale_x_continuous(expression(Number~of~days~sampled~(log[2]~scale)),
                     trans = 'log2', breaks = c(2, 16, 128, 1024),
                     limits = c(2, 1100)) +
  scale_y_log10(expression(Estimated~home~range~(log[10]~scale)))
```

```{r, eval=TRUE, echo=FALSE, fig.cap="Estimated spatial needs as a function of the number of days sampled for an animal in a habitat with the highest $\\e(R)$ and lowest $\\var(R)$ (left) and an animal with the lowest $\\e(R)$ and highest $\\var(R)$ (right). In both cases, 100 days are sufficient to produce stable estimates of spatial needs."}
knitr::include_graphics('H:/GitHub/hr-resource-stoch/figures/hr-over-days.png',
                        rel_path = FALSE)
```

@@

This final section illustrates the location-scale GAM used to estimate the effects of resource abundance and stochasticity on the simulated spatial needs. Although the model was fit to both the 95% and core (50%) home range estimates, the results were presented only for the 95% quantile for simplicity. The home range was caulculated using a Gaussian approximation using the simulated organism's positional variance:

@@

and therefore $\e(R)$ and $\var(R)$ would have similar effects (but about 4.322 times weaker) on the core home range than they do on the 95% home range. Note that we used this approximation because, unlike real organisms, the simulated organism did not use the available space selectively (e.g., spending more time near cell boundaries), so the Gaussian approximation is appropriate. When estimating spatial needs based on empirical data, we suggest estimating utilization distributions using methods such as Autocorrelated Kernel Density Estimation [see Appendix 3 on empirical modeling and @noonan_comprehensive_2019; @alston_mitigating_2022; @silva_autocorrelationinformed_2022].

@@

The abundance of data for the average $\e(R)$ and $\var(R)$ did not create biases in the models, since removing such values had no appreciable effect on the model estimates (not shown). To estimate the effects of resource abundance and stochasticity on the simulated spatial needs, we fit 3 location-scale GAMs (GAMLSs) with a location-scale gamma distribution (since home ranges are strictly positive) of increasing complexity. We hypothesized that the effect of $\e(R)$ would depend on $\var(R)$ (and the effect of $\var(R)$ would depend on $\e(R)$), since we expected organisms to respond to changes in $\mu(t)$ less in predictable environments than in stochastic ones. The three models are detailed below and compared using the Akaike Information Criterion and the Bayesian Information Criterion. Both information criteria demonstrate that the third model, which accounts for the interaction effects of $\e(R)$ and $\var(R)$, is the best model.

>>>>

---
title: \large How resource abundance and stochasticity affect animals' space-use requirements
subtitle: "Appendix 2: Simulations"
author:
  - name: Stefano Mezzini
    email: stefano.mezzini@ubc.ca
    institute: [biol, braes]
  - name: Simon Wood
    institute: uofe
  - name: E. Patrícia Medici
    institute: [tapir, iucn, escas]
  - name: Michael J. Noonan
    email: michael.noonan@ubc.ca
    institute: [biol, braes, cmps]
institute:
  - biol: Department of Biology, The University of British Columbia Okanagan, Kelowna, British Columbia, Canada.
  - braes: Okanagan Institute for Biodiversity, Resilience, and Ecosystem Services, The University of British Columbia Okanagan, Kelowna, British Columbia, Canada.
  - uofe: School of Mathematics, James Clerk Maxwell Building, University of Edinburgh, Edinburgh, Unted Kingdom.
  - tapir: Lowland Tapir Conservation Initiative (LTCI), Instituto de Pesquisas Ecológicas (IPÊ), Rodovia Dom Pedro I, km 47, Nazaré Paulista, São Paulo 12960-000, Brazil.
  - iucn: IUCN SSC Tapir Specialist Group (TSG), Campo Grande, Brazil.
  - escas: Escola Superior de Conservação Ambiental E Sustentabilidade (ESCAS/IPÊ), Rodovia Dom Pedro I, km 47, Nazaré Paulista, São Paulo 12960-000, Brazil.
  - cmps: Department of Computer Science, Math, Physics, and Statistics, The University of British Columbia Okanagan, Kelowna, British Columbia, Canada.
bibliography: 'hr-resource-stoch.bib'
csl: 'the-american-naturalist.csl'
fontsize: 12pt
header-includes:
    - \usepackage{setspace}\doublespacing # for double-spaced text
    - \usepackage[small]{titlesec} # for smaller font for headings
    - \usepackage{caption} # for more customization of captions
    - \captionsetup[figure]{font=scriptsize} # smaller caption text
    - \usepackage{hanging} # for hanging indents in references
subparagraph: true # needed for \usepackage[small]{titlesec}
output:
  bookdown::pdf_document2:
    toc: false
    pandoc_args:
      - '--lua-filter=scholarly-metadata.lua' # for author affiliations
      - '--lua-filter=author-info-blocks.lua' # for author affiliations
---

@@

```{r 5-5-sims, eval=TRUE, echo=FALSE, fig.cap="Simulated home range sizes, $H$, of an organism living in habitats where the mean and variance in resources are constant, linearly increasing, cyclical, drifting, or erratic over time (and homogenous over space). Note how $H$ decreases nonlinearly as $\\mu(t)$ increases and increases nonlinearly as $\\sigma^2(t)$ increases. Additionally, the variance in $H$ is higher when $\\mu(t)$ is lower or $\\sigma^2(t)$ is higher, and changes in $\\sigma^2(t)$ have greater impacts when $\\mu(t)$ is low.", out.width='100%', cache=FALSE}
knitr::include_graphics('../figures/mean-variance-5-by-5-hr-sims.png',
                        rel_path = FALSE)
```

```{r 5-5-reg, eval=TRUE, echo=FALSE, fig.cap="Effects of $\\e(R)$ and $\\var(R)$ on simulated space-use requirements. The relationships were estimated using a Generalized Additive Model for Location and Scale (GAMLS; Rigby and Stasinopoulos 2005; Stasinopoulos and Rigby 2007) with a Gamma location-scale family of distributions ($\\tt{mgcv\\!::\\!gammals})$. The model accounted for the effects of $\\e(R)$ and $\\var(R)$ and the interaction effects between the two on both the location (i.e., mean) of $H$ and its scale parameter. Note the nonlinear decrease in $H$ as $\\e(R)$ increases and the increase in $H$ as $\\var(R)$ increases. Additionally, note how the variance in space-use requirements strongly increases with mean space-use requirements.", out.width='100%', cache=FALSE}
knitr::include_graphics('../figures/simulation-regression-plots.png',
                        rel_path = FALSE)
```

@@

```{r sims-example, echo=FALSE, eval=TRUE, fig.cap="Overview of how animals' space-use requirements were simulated. (a.) Tracks were simulated using an Integrated Ornstein-Uhlenbeck model (IOU model, an infinitely diffusive and continous-velocity movement model), starting from the point $\\langle 0, 0 \\rangle$ (black and yellow square). (b.) Each time the track crossed into a new cell (green dots), the animal collected a random amount of resources that followed a Gamma distribution with common mean $\\mu (t)$ and variance $\\sigma^2 (t)$. (c.) Each time the animal collected more resources, its satiety (purple) increased. Once the animal collected sufficient resources, the animal stopped moving (i.e., the track was truncated). (d.) The process was repeated $2^{10}=1024$ times (13 tracks pictured in this panel). (e.) The final set of (truncated) tracks was then modeled using Ornstein-Uhlenbeck Foraging models to estimate the 95\\% home range estimates using Autocorrelated Kernel Density Estimates.", out.width='100%', fig.pos='!h', cache=FALSE}
knitr::include_graphics('H:/GitHub/hr-resource-stoch/figures/simulation-example.png',
                        rel_path = FALSE)
```

@@

```{r dt-sensitivity, fig.cap="Exploratory plots used to decide an appropriate sampling interval. (a.) Histograms of the number of encounters as a function of the interval between encounters, with a binwith of 30 seconds. Although some encounters occur with less than 30 seconds between them, approximately 93\\% of them occur at least 30 seconds apart. (b.) Number of detected encounters as a function of sampling interval. The colored lines indicate the estimated relationship based on a Generalized Additive Model fit using the $\\tt{geom\\_smooth}$ function from the $\\tt{ggplot2}$ package. Although the number of encounters detected decreases as sampling interval doubles, the loss at $\\Delta = 30$s is negligible. (c.) Beginning of the track generated with seed \"1\" (purple line) for different sampling intervals. Red dots indicate locations where the animal remained in the same cell, while the blue squares indicate when an animal was in a new cell and thus encountered food. While the number of encounters detected decreases as the sampling interval increases, most of the encounters lost at $\\Delta t = 30$s occured because the animal remained almost adjacent to the borders between cells. Additionally, the track at $\\Delta t = 30$s is still sufficiently tortuous to represent realistic animal movement. (d.) The three tracks used in these tests over the raster used for determining when the animals encountered food.", out.width='100%', echo=FALSE, eval=TRUE, cache=FALSE}
knitr::include_graphics('H:/GitHub/hr-resource-stoch/figures/thinning-examples.png',
                        rel_path = FALSE)
```

@@

In this script, we check how many tracks are necessary to produce stable and accurate estimates of the space-use requirements. We do so by estimating the home ranges of animals for varying numbers of track in the best-case scenario (highest $\e(R)$ and lowest $\var(R)$) and worst-case scenario (lowest $\e(R)$ and highest $\var(R)$).

@@

ggplot(saturation_days, aes(n_days, hr)) +
  facet_wrap(~ case, nrow = 1) +
  geom_vline(xintercept = 100, color = 'darkorange') +
  geom_smooth(method = 'gam', color = 'black',
              formula = y ~ s(x, bs = 'cs', k = 10),
              method.args = list(family = Gamma(link = 'log'))) +
  geom_point(alpha = 0.3) +
  scale_x_continuous(expression(Number~of~days~sampled~(log[2]~scale)),
                     trans = 'log2', breaks = c(2, 16, 128, 1024),
                     limits = c(2, 1100)) +
  scale_y_continuous(expression(atop(Estimated~'space-use',
                                     requirements~(log[2]~scale))),
                     trans = 'log2')
```

```{r, eval=TRUE, echo=FALSE, fig.cap="Estimated space-use requirements as a function of the number of days sampled for an animal in a habitat with the highest $\\e(R)$ and lowest $\\var(R)$ (left) and an animal with the lowest $\\e(R)$ and highest $\\var(R)$ (right). In both cases, 100 days are sufficient to produce stable estimates of space-use requirements.", cache=FALSE}
knitr::include_graphics('H:/GitHub/hr-resource-stoch/figures/hr-over-days.png',
                        rel_path = FALSE)
```

@@

This final section illustrates the location-scale GAM used to estimate the effects of resource abundance and stochasticity on the simulated space-use requirements. Although the model was fit to both the 95% and core (50%) home range estimates, the results were presented only for the 95% quantile for simplicity. The home range was caulculated using a Gaussian approximation using the simulated organism's positional variance:

@@

and therefore $\e(R)$ and $\var(R)$ would have similar effects (but about 4.322 times weaker) on the core home range than they do on the 95% home range. Note that we used this approximation because, unlike real organisms, the simulated organism did not use the available space selectively (e.g., spending more time near cell boundaries), so the Gaussian approximation is appropriate. When estimating space-use requirements based on empirical data, we suggest estimating utilization distributions using methods such as Autocorrelated Kernel Density Estimation [see Appendix 3 on empirical modeling and @noonan_comprehensive_2019; @alston_mitigating_2022; @silva_autocorrelationinformed_2022].

@@

The abundance of data for the average $\e(R)$ and $\var(R)$ did not create biases in the models, since removing such values had no appreciable effect on the model estimates (not shown). To estimate the effects of resource abundance and stochasticity on the simulated space-use requirements, we fit 3 location-scale GAMs (GAMLSs) with a location-scale gamma distribution (since home ranges are strictly positive) of increasing complexity. We hypothesized that the effect of $\e(R)$ would depend on $\var(R)$ (and the effect of $\var(R)$ would depend on $\e(R)$), since we expected organisms to respond to changes in $\mu(t)$ less in predictable environments than in stochastic ones. The three models are detailed below and compared using the Akaike Information Criterion and the Bayesian Information Criterion. Both information criteria demonstrate that the third model, which accounts for the interaction effects of $\e(R)$ and $\var(R)$, is the best model.
